### 2013-12-13 regressionModelling.Rmd
Some Sunday evening edits..
Makromuuttujat lukittu gdoChange,hdi,voice&Account
Makromuuttujat nyt lukittu
1) bkt-muutos 2007-2010
2) HDI
3) Voice and accountability (WB)

perusteet:
1) makrotalouden muutos kriisin aikana
2) elinolojen indikaattori
3) demokratiaindikaattori

Lisäsin ko, muuttujat paperin hajontakuvioihin ja lisäsin ekaan mallitaulukkoon molempiin malleihin sarakkeen jossa vaan makrot.

```{r, eval=FALSE, echo=FALSE}
library(knitr)
library(markdown)
knit2html('regressionModelling.Rmd', 
          stylesheet="~/workspace/web/css/rmarkdown.css",
          options = c('toc', markdown::markdownHTMLOptions(TRUE)))

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

```{rmultilevelLoadData}
#########################################
#########################################
setwd("~/workspace/lits/attributions/")

@@

```{rmultilevelBivarSoc}
library(lme4)
df.model$group_balinCis[df.model$cntry %in% c('Czech Republic',
                                        'Hungary','Bulgaria',
                                        'Poland','Slovakia',
                                        'Slovenia','Romania')] <- 'CEE'

@@

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
# bisoc.8 <- glmer(pov.log.social ~ perGini+(1|cntry),
#                         family = binomial(logit), data = df.model)
bisoc.9 <- glmer(pov.log.social ~ gdpChange+(1|cntry),
                         family = binomial(logit), data = df.model)
bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.social ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

```{rmultilevelBivarSocOutputNOCI, results='asis'}

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      #"Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod",
                     "Perceived Gini")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          #bisoc.8,
          bisoc.9,bisoc.10,
          bisoc.11,bisoc.12,
          bisoc.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
#biind.8 <- glmer(pov.log.individual ~ perGini+(1|cntry),
#                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpChange+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
biind.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
biind.13 <- glmer(pov.log.individual ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

```{rmultilevelBivarIndOuputNOCI, results='asis'}

library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          #biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

```{rmultilevelMultiSoc}
library(lme4)

soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                      data = df.model)
soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiSocOutputNOCI, results='asis'}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Perceived Gini",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi = c("Empty",
                      "Only individual",
                      "Gini added",
                      "GDP change added",
                      "Good governance added")

@@

```{rmultilevelMultiInd}
ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultivarFull}

soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

socVsInc <- glmer(pov.log.socVsInc ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

save(ind.0,ind.1,ind.2,ind.3,ind.4,
     soc.0,soc.1,soc.2,soc.3,soc.4,
     socVsInc, file="data/finalModels.RData")

@@

```{rmultilevelMultivarSlideOutput, results='asis', eval=TRUE}
library(texreg)
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi = c("Empty",
                      "Only individual",
                      "Gini added",
                      "GDP change added",
                      "Good governance added")

@@

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

>>>>

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=FALSE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

```{rmultilevelLoadData, eval=TRUE}
#########################################
#########################################
setwd("~/workspace/lits/attributions/")

@@

```{rmultilevelBivarSoc, eval=TRUE}
library(lme4)
df.model$group_balinCis[df.model$cntry %in% c('Czech Republic',
                                        'Hungary','Bulgaria',
                                        'Poland','Slovakia',
                                        'Slovenia','Romania')] <- 'CEE'

@@

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
bisoc.8 <- glmer(pov.log.social ~ undp_hdi+(1|cntry),
                         family = binomial(logit), data = df.model)
bisoc.9 <- glmer(pov.log.social ~ gdpChange+(1|cntry),
                         family = binomial(logit), data = df.model)
bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.13 <- glmer(pov.log.social ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)

@@

```{rmultilevelBivarSocOutputNOCI, results='asis', eval=TRUE}

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Development Index",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod",
                     "Perceived Gini")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
          bisoc.11,bisoc.12,
          bisoc.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd, eval=TRUE}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ undp_hdi+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpChange+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
biind.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)
biind.13 <- glmer(pov.log.individual ~ perGini+(1|cntry),
                          family = binomial(logit), data = df.model)
```

```{rmultilevelBivarIndOuputNOCI, results='asis', eval=TRUE}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

```{rmultilevelMultiSoc, eval=TRUE}
library(lme4)
soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                      data = df.model)
soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.Cont <- glmer(pov.log.social ~ undp_hdi+gdpChange+
                      wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiSocOutputNOCI, results='asis', eval=TRUE}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Deveplopment Index",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi = c("Empty",
                      "Only individual",
                      "HDI added",
                      "GDP change added",
                      "Good governance added")

@@

```{rmultilevelMultiInd, eval=TRUE}
ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.Cont <- glmer(pov.log.individual ~ undp_hdi+gdpChange+
                      wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiIndOutputNOCI, results='asis', eval=TRUE}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultivarFull, eval=TRUE}

soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

socVsInc <- glmer(pov.log.socVsInc ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        undp_hdi+gdpChange+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

save(ind.0,ind.1,ind.2,ind.3,ind.4,ind.Cont,
     soc.0,soc.1,soc.2,soc.3,soc.4,soc.Cont,
     socVsInc, file="data/finalModels.RData")

@@

```{rmultilevelMultivarSlideOutput, results='asis', eval=TRUE, eval=TRUE}
library(texreg)
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Development Index",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi = c("Empty",
                      "Only individual",
                      "HDI added",
                      "GDP change added",
                      "Good governance added")

@@

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Development Index",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")
